---
title: "HW3"
author: "Samane Khademi"
date: "2022-09-16"
output: html_document
---


[Link](https://rpubs.com/Samane65/943155) to rPub


[Link](https://github.com/Samane86/607-HW3) to GitHub

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the required libraries:
```{r}
require(dplyr)
library(stringr)

```

# 1
Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset, provide code that identifies the majors that contain either "DATA" or "STATISTICS".

First let's load the data:

```{r}
MajorsList <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv",
                       header=TRUE,stringsAsFactors=FALSE)
```

It's better to take a look to our data to see how many columns and rows do we have:

```{r}
str(MajorsList)
```

Now we can extract the desired words in our data:

```{r}
str_subset(MajorsList$Major, "DATA|STATISTICS")
```


We have three majors that contain either "DATA" or "STATISTICS".

# 2

Write code that transforms the data below:


```{r}
vec <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    


[13] "olive"        "salal berry"'

vec

```


```{r}
vec2 <- str_extract_all(vec, pattern = '[A-Za-z]+.?[A-Za-z]+')
vec2
```




```{r}
vec3 <- str_c(vec2, collapse = ", ")
vec3
```

Since printed representation of a string is not the same as string itself, because the printed representation shows the escapes. To see the raw contents of the string, use writeLines():

```{r}
writeLines(vec3)
```

 
# 3
 
### Describe, in words, what these expressions will match:

Let's usethe common words in stringr::words, suggested by the r4ds book:

```{r}
w <- stringr::words
```

(.)\1\1  __>  The same character appearing three times in a row. Like:"fff" or "888"

```{r}
str_subset(w, "(.)\1\1" )
```



"(.)(.)\\2\\1" __> A pair of characters followed by the second character first,
and then the first character. Like "3dd3" or "j//j"

```{r}
str_subset(w, "(.)(.)\\2\\1" )
```

(..)\1   __> Two characters  repeated. Like "cdcd" or "#e#e"

```{r}
str_subset(w, "(..)\1" )
```

"(.).\\1.\\1" __> One character followed by any character, then the first character again,
then any other character and then the first character again. Like: "s!sms" or "/g/a/"

```{r}
str_subset(w, "(..)\1" )
```


"(.)(.)(.).*\\3\\2\\1"  __> Three characters followed by zero or more characters of all kind, And then same three characters but in reverse order. Like "234jdhfj432" or "blabla"

```{r}
str_subset(w, "(..)\1" )
```


# 4

Construct regular expressions to match words that:
  

a) Start and end with the same character.

```{r}
str_subset(w, "^(.)((.*\\1$)|\\1?$)")

```



b) Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)

```{r}
str_subset(w, "([A-Za-z][A-Za-z]).*\\1")
```

c) Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r}
str_subset(w, "([A-Za-z]).*\\1.*\\1.*")
```




